A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-10-21 Simulator/article.tex
la2pdf commit - 2015:10:21	13:19:57	(Wed21.Oct)

One of the major shortcomings of autonomous underwater vehicles (AUVs) is their lack of curiosity. When encountering an interesting object, an AUV with a mounted sonar imaging system should be able to detect it, and perhaps move in for closer examination. Besides the apparent challenge of trying to detect something with a long list of unknown parameters, this must happen in real-time and be very power efficient.

>>>>

One of the major shortcomings of autonomous underwater vehicles (AUVs) is their lack of intelligence. When encountering an interesting object, an AUV mounted with a sonar imaging system should be able to tell that this object might be worth closer examination, and act accordingly. This is challenging as what we deem as interesting is often something that stand out form the background, i.e. it relies on previous knowledge. It would also need to process this information is near real-time to act in an efficient manner.
